---
title: "For Live Session 1"
author: "Zachary Jennings"
date: "2026-01-02"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Scientist Profile

```{r profile}
cat <- c("Data\nViz","ML","Math","Stats","Comp\nSci","Comm","Domain\nExpertise")

ratings <- c(80, 10, 60, 50, 30, 90, 90)
par(las=1)
barplot(ratings, names.arg= cat,
        main = "Data Scientist Profile",
        col = "skyblue",
        ylim=c(0,100),
        yaxt="n",
        space=2)
```

# CLT

## Generate Chi Sq distribution for Population of 10M with 2 df
```{r population}
population = rchisq(10000000,2)
```

## Generate histogram of population to show skewness

```{r}
hist(population, col = "skyblue")
```

## Record mean and sd of population

```{r}
mean(population)
sd(population)
```

#### CLT suggests taking sample means of sample size 50 should produce a normal distribution of sample means

#### The means should approximate mu and the standard deviation should equal s/ sq rt of 'n'

#### Calculate 10,000 samples of size 50 from population with histogram of sample means
```{r}
simulations = 10000 #number of iterations
sample_size = 50    #sample size of each iteration

xBarVec = c() #global vector to hold sample means

#loop to instantiate xBarVec means for simulation
for (i in 1:simulations) {
  sample1 = sample(population, sample_size)
  xbar = mean(sample1)
  xBarVec = c(xBarVec, xbar)
}

#histogram of distribution of sample means
hist(xBarVec, col = "blue", 
     main = "Distribution of Sample Means",
     xlab = "x-Bar")

#display standard error of distribution of sample means
sd(xBarVec)
```

## Conduct hypothesis test for Beach Comber dataset

```{r beachcomber_hypothesis_test}
#?t.test #learn more about t-test function usage

ages = c(25,19,37,29,40,28,31) #vector containing ages of patrons

t.test(ages,mu=21, conf.level=0.95) #t.test of ages vector with Ho -> mu=21 at alpha=0.05
```